Millions of Type Errors

### 2023-03-17 oopsla23/paper.tex
Add more text to intro

millions of creators:
 gradual types,
 success types,
 semantic subtyping

millions (?) of telemetry records

takeaways about adoption,
 errors by mode (nocheck, nonstrict, strict),
 patterns of use,

>>>>

\anon{Roblox Studio} has a telemetry system, which is used to guage
the effectiveness of creation features. This system stochastically
determines which sessions should report telemety, and for those
sessions, reports telemetry records back with a summary of the
session. In the case of this study, the telemetry includes data on the
number of errors at various levels of granularity: in the current edit
region, in the current file, and in every file which was type
checked.

The telemetry data we analyzed does not contain any Personally
Identifying Information. There is no record of the creator's identity,
geographic location, IP address, or which creation they worked on.
Telemetry records are correlated by session, using a pseudonymized
session identifier.

Most users of \anon{Roblox Studio} do not opt in to type error
reporting, and so they do not see the ``squiggly underlining'' that
indicates a type error site. Nonetheless, the type inference system
still runs (since it drives automplete and other type-based tools) and
so we can record which type errors would have been reported had the
user enabled type error reporting. As a result, we can investigate
which type errors are  fixed by users, even if they did not opt in to
type error reporting.

\textbf{Ben: give an outline of our RQs here.}

This paper is the first to use telemetry as a mechanism for
large-scale measurement of the effectiveness of type error reporting.
Our data captures \textbf{XX} sessions, for a total of \textbf{YY}
hours and \textbf{ZZ} type errors.

Telemetry cannot replace user studies, as there is no way to measure
creator sentiment, but provide complementary data at scale.
